---
title: "Presentaciones SAE"
author: "Yelena"
date: "2025-12-22"
output: html_document
---

```{r setup, include=FALSE}
library(psych)
library(dplyr)
library(purrr)
library(ggplot2)
library(knitr)
library(kableExtra)

## Load the processed dataset created in `script/proc_data.R`
## This runs the preprocessing script and then extracts the `data` object it creates.
proc_env <- new.env(parent = globalenv())
source(here::here("script/proc_data.R"), local = proc_env)
data <- proc_env$data
stopifnot(exists("data", envir = proc_env), !is.null(data))

# Variables de interes
sae_pre_comp_obj <- select(data, starts_with("sae_pre_comp_obj"))
sae_pos_comp_obj <- select(data, starts_with("sae_pos_comp_obj"))
sae_pre_comp_subj <- select(data, starts_with("sae_pre_comp_subj"))
sae_pos_comp_subj <- select(data, starts_with("sae_pos_comp_subj"))
sae_pre_trust_belief_reliab <- select(data, starts_with("sae_pre_trust_belief_reliab"))
sae_pos_trust_belief_reliab <- select(data, starts_with("sae_pos_trust_belief_reliab"))
sae_pre_trust_belief_func <- select(data, starts_with("sae_pre_trust_belief_func"))
sae_pos_trust_belief_func <- select(data, starts_with("sae_pos_trust_belief_func"))
sae_pre_trust_belief_help <- select(data, starts_with("sae_pre_trust_belief_help"))
sae_pos_trust_belief_help <- select(data, starts_with("sae_pos_trust_belief_help"))
sae_pre_trust_func_reliab <- select(data, starts_with("sae_pre_trust_func_reliab"))
sae_pos_trust_func_reliab <- select(data, starts_with("sae_pos_trust_func_reliab"))
sae_pre_trust_func_capab <- select(data, starts_with("sae_pre_trust_func_capab"))
sae_pos_trust_func_capab <- select(data, starts_with("sae_pos_trust_func_capab"))
sae_pre_trust_moral_ethi <- select(data, starts_with("sae_pre_trust_moral_ethi"))
sae_pos_trust_moral_ethi <- select(data, starts_with("sae_pos_trust_moral_ethi"))
sae_pre_trust_moral_sinc <- select(data, starts_with("sae_pre_trust_moral_sinc"))
sae_pos_trust_moral_sinc <- select(data, starts_with("sae_pos_trust_moral_sinc"))
```


```{r calcular_cronbach, include=FALSE}
# Function to calculate descriptive statistics - returns a tibble with the statistics
describe_stats <- function(data) {
  # Calculate the mean for each respondent (row-wise mean)
  row_means <- rowMeans(data, na.rm = TRUE)
  
  # Calculate overall statistics from these row means
  overall_mean <- mean(row_means, na.rm = TRUE)
  overall_median <- median(row_means, na.rm = TRUE)
  overall_sd <- sd(row_means, na.rm = TRUE)
  overall_min <- min(row_means, na.rm = TRUE)
  overall_max <- max(row_means, na.rm = TRUE)
  
  # Calculate Cronbach's alpha (psych::alpha) and extract only the raw_alpha
  alpha_val <- psych::alpha(data)$total$raw_alpha

  tibble(
    cronbach_alpha = alpha_val,
    mean = overall_mean,
    median = overall_median,
    std = overall_sd,
    min = overall_min,
    max = overall_max
  )
}

# For each of the variables, calculate cronbach's alpha, mean, median, std, min, max
pre_stats_obj_sae <- describe_stats(sae_pre_comp_obj)
pos_stats_obj_sae <- describe_stats(sae_pos_comp_obj)
pre_stats_subj_sae <- describe_stats(sae_pre_comp_subj)
pos_stats_subj_sae <- describe_stats(sae_pos_comp_subj)
pre_stats_trust_belief_reliab_sae <- describe_stats(sae_pre_trust_belief_reliab)
pos_stats_trust_belief_reliab_sae <- describe_stats(sae_pos_trust_belief_reliab)
pre_stats_trust_belief_func_sae <- describe_stats(sae_pre_trust_belief_func)
pos_stats_trust_belief_func_sae <- describe_stats(sae_pos_trust_belief_func)
pre_stats_trust_belief_help_sae <- describe_stats(sae_pre_trust_belief_help)
pos_stats_trust_belief_help_sae <- describe_stats(sae_pos_trust_belief_help)
pre_stats_trust_func_reliab_sae <- describe_stats(sae_pre_trust_func_reliab)
pos_stats_trust_func_reliab_sae <- describe_stats(sae_pos_trust_func_reliab)
pre_stats_trust_func_capab_sae <- describe_stats(sae_pre_trust_func_capab)
pos_stats_trust_func_capab_sae <- describe_stats(sae_pos_trust_func_capab)
pre_stats_trust_moral_ethi_sae <- describe_stats(sae_pre_trust_moral_ethi)
pos_stats_trust_moral_ethi_sae <- describe_stats(sae_pos_trust_moral_ethi)
pre_stats_trust_moral_sinc_sae <- describe_stats(sae_pre_trust_moral_sinc)
pos_stats_trust_moral_sinc_sae <- describe_stats(sae_pos_trust_moral_sinc)
```

Alfa de Cronbach para cuestionarios de SAE
```{r tabla_std_descrip, echo=FALSE}
# Create a table with the statistics for each variable
stats_table <- list(
  #sae_pre_comp_obj = pre_stats_obj_sae,
  #sae_pos_comp_obj = pos_stats_obj_sae,
  sae_pre_comp_subj = pre_stats_subj_sae,
  sae_pos_comp_subj = pos_stats_subj_sae,
  sae_pre_trust_belief_reliab = pre_stats_trust_belief_reliab_sae,
  sae_pos_trust_belief_reliab = pos_stats_trust_belief_reliab_sae,
  sae_pre_trust_belief_func = pre_stats_trust_belief_func_sae,
  sae_pos_trust_belief_func = pos_stats_trust_belief_func_sae,
  sae_pre_trust_belief_help = pre_stats_trust_belief_help_sae,
  sae_pos_trust_belief_help = pos_stats_trust_belief_help_sae,
  sae_pre_trust_func_reliab = pre_stats_trust_func_reliab_sae,
  sae_pos_trust_func_reliab = pos_stats_trust_func_reliab_sae,
  sae_pre_trust_func_capab = pre_stats_trust_func_capab_sae,
  sae_pos_trust_func_capab = pos_stats_trust_func_capab_sae,
  sae_pre_trust_moral_ethi = pre_stats_trust_moral_ethi_sae,
  sae_pos_trust_moral_ethi = pos_stats_trust_moral_ethi_sae,
  sae_pre_trust_moral_sinc = pre_stats_trust_moral_sinc_sae,
  sae_pos_trust_moral_sinc = pos_stats_trust_moral_sinc_sae
) |>
  imap_dfr(\(stats, var_name) dplyr::mutate(stats, Variable = var_name)) |>
  
  mutate(
    grupo = str_remove(Variable, "sae_pre_|sae_pos_"),
    momento = ifelse(str_detect(Variable, "pre"), 1, 2)
  ) |>
  # DEFINIMOS EL ORDEN DE LOS GRUPOS AQUÍ
  mutate(grupo = factor(grupo, levels = c(
    "comp_obj", "comp_subj", 
    "trust_belief_func", "trust_belief_reliab", # McKnight_Func
    "trust_belief_help",                        # McKnight_Moral
    "trust_func_capab", "trust_func_reliab",    # MDMT_Func
    "trust_moral_ethi", "trust_moral_sinc"      # MDMT_Moral
  ))) |>
  arrange(grupo, momento) |> 
  # ASIGNAMOS NOMBRES DESCRIPTIVOS AQUÍ
  mutate(Variable = case_when(
    #Variable == "sae_pre_comp_obj" ~ "Comprensión objetiva (pre)",
    #Variable == "sae_pos_comp_obj" ~ "Comprensión objetiva (post)",
    Variable == "sae_pre_comp_subj" ~ "Comprensión subjetiva (pre)",
    Variable == "sae_pos_comp_subj" ~ "Comprensión subjetiva (post)",
    Variable == "sae_pre_trust_belief_reliab" ~ "Trust McKnight_Func: Reliability (pre)",
    Variable == "sae_pos_trust_belief_reliab" ~ "Trust McKnight_Func: Reliability (post)",
    Variable == "sae_pre_trust_belief_func" ~ "Trust McKnight_Func: Functionality (pre)",
    Variable == "sae_pos_trust_belief_func" ~ "Trust McKnight_Func: Functionality (post)",
    Variable == "sae_pre_trust_belief_help" ~ "Trust McKnight_Moral: Helpfulness (pre)",
    Variable == "sae_pos_trust_belief_help" ~ "Trust McKnight_Moral: Helpfulness (post)",
    Variable == "sae_pre_trust_func_reliab" ~ "Trust MDMT_Func: Reliability (pre)",
    Variable == "sae_pos_trust_func_reliab" ~ "Trust MDMT_Func: Reliability (post)",
    Variable == "sae_pre_trust_func_capab" ~ "Trust MDMT_Func: Capacity (pre)",
    Variable == "sae_pos_trust_func_capab" ~ "Trust MDMT_Func: Capacity (post)",
    Variable == "sae_pre_trust_moral_ethi" ~ "Trust MDMT_Moral: Ethic (pre)",
    Variable == "sae_pos_trust_moral_ethi" ~ "Trust MDMT_Moral: Ethic (post)",
    Variable == "sae_pre_trust_moral_sinc" ~ "Trust MDMT_Moral: Sincerity (pre)",
    Variable == "sae_pos_trust_moral_sinc" ~ "Trust MDMT_Moral: Sincerity (post)",
    TRUE ~ Variable # Por si olvidas alguna, deja el nombre original
  )) |>
  select(Variable, everything(), -grupo, -momento) |>
  rename(
    "Cronbach alpha" = cronbach_alpha,
    "Mean" = mean,
    "Median" = median,
    "Std" = std,
    "Min" = min,
    "Max" = max
  )

stats_table %>%
  mutate(across(where(is.numeric), ~ round(as.numeric(.), 3))) %>%
  kableExtra::kbl(caption = "Estadísticas descriptivas de las variables (Pre vs Post)", booktabs = TRUE) %>%
  kableExtra::kable_styling(
    bootstrap_options = c("hover", "condensed"),
    full_width = F,
    position = "left"
    ) %>%
  kableExtra::column_spec(1, width = "100px", bold = TRUE) %>% #ancho primera columna
  # Color para filas PRE (impares)
  kableExtra::row_spec(seq(1, nrow(stats_table), 2), background = "#f9f9f9") %>%
  # Color para filas POS (pares) y línea divisoria
  kableExtra::row_spec(seq(2, nrow(stats_table), 2), 
                       background = "#ffffff", 
                       extra_css = "border-bottom: 2px solid #666;")

  #dplyr::select(Variable, dplyr::everything()) |>
  #dplyr::arrange(Variable) |>
  #dplyr::rename(
  #  "Cronbach alpha" = cronbach_alpha,
  #  "Mean" = mean,
  #  "Median" = median,
  #  "Std" = std,
  #  "Min" = min,
  #  "Max" = max
  #)

knitr::kable(stats_table, caption = "Estadísticas descriptivas de las variables")
```


```{r create_ANOVA, include=FALSE}
# Function to create a two way ANOVA plot for a pair of variable matrices
make_anova2_plot <- function(
  data1,
  data2,
  label1 = deparse(substitute(data1)),
  label2 = deparse(substitute(data2)),
  paired = FALSE,
  ci_level = 0.95,
  y_limits = c(1, 5),
  y_breaks = 1:5
) {
  # Coerce to numeric safely (handles character likert "1".."5"; avoids factor->integer codes)
  to_numeric_df <- function(x) {
    x <- as.data.frame(x)
    x[] <- lapply(x, function(col) suppressWarnings(as.numeric(as.character(col))))
    x
  }

  d1 <- to_numeric_df(data1)
  d2 <- to_numeric_df(data2)

  # Row-wise mean per respondent
  row_means1 <- rowMeans(d1, na.rm = TRUE)
  row_means2 <- rowMeans(d2, na.rm = TRUE)

  # Summary stats + CI for plotting
  summarize_with_ci <- function(x) {
    x <- x[!is.na(x)]
    n <- length(x)
    m <- mean(x)
    s <- stats::sd(x)
    se <- s / sqrt(n)
    alpha <- 1 - ci_level
    tcrit <- stats::qt(1 - alpha / 2, df = n - 1)
    ci <- tcrit * se
    tibble(n = n, mean = m, sd = s, se = se, ci = ci, ymin = m - ci, ymax = m + ci)
  }

  sum1 <- summarize_with_ci(row_means1) |> mutate(Variable = label1)
  sum2 <- summarize_with_ci(row_means2) |> mutate(Variable = label2)
  summary_df <- bind_rows(sum1, sum2) |>
    mutate(
      Variable = factor(Variable, levels = c(label1, label2)),
      label = sprintf("Mean=%.2f\nSD=%.2f", mean, sd)
    )

  # Statistical test (with 2 groups this is equivalent to 1-way ANOVA)
  # If you truly need a 2-way ANOVA (2 factors), we can extend this signature.
  test_df <- tibble(
    value = c(row_means1, row_means2),
    Variable = factor(c(rep(label1, length(row_means1)), rep(label2, length(row_means2))),
                      levels = c(label1, label2))
  ) |>
    filter(!is.na(value))

  # Use the vector form so `paired` is supported (formula method doesn't accept `paired`)
  rm1 <- test_df$value[test_df$Variable == label1]
  rm2 <- test_df$value[test_df$Variable == label2]

  test <- if (paired) {
    # paired requires equal-length vectors (same respondents in same order)
    stats::t.test(rm1, rm2, paired = TRUE)
  } else {
    stats::t.test(rm1, rm2, paired = FALSE)
  }

  # Nudge labels slightly above the error bar tops
  label_nudge_y <- if (!is.null(y_limits) && length(y_limits) == 2) {
    0.03 * diff(y_limits)
  } else {
    0.03 * (max(summary_df$ymax, na.rm = TRUE) - min(summary_df$ymin, na.rm = TRUE))
  }

  p <- ggplot(summary_df, aes(x = Variable, y = mean, group = 1)) +
    geom_line(linewidth = 0.8) +
    geom_point(size = 2.8) +
    geom_errorbar(aes(ymin = ymin, ymax = ymax), width = 0.15, linewidth = 0.8) +
    geom_text(aes(y = ymax, label = label), vjust = 0, nudge_y = label_nudge_y, size = 3.3) +
    labs(x = NULL, y = "Mean (row-wise)") +
    theme_classic(base_size = 12)

  if (!is.null(y_limits)) {
    p <- p + coord_cartesian(ylim = y_limits, clip = "off")
  }
  if (!is.null(y_breaks)) {
    p <- p + scale_y_continuous(breaks = y_breaks)
  }

  list(
    plot = p,
    summary = summary_df,
    test = test
  )
}
```

ANOVA H2: Explanations that include algorithm disclosure generate greater a) subjective and objective understanding, as well as b) functional and moral trust, than explanations that do not include it.
```{r disclosure_subjective, echo=FALSE}
#names_to_plot <- c("Sin revelación", "Con revelación")

pos_subj_sae_AlgD_0 <- data %>%
  filter(disclosure == 0) %>%
  select(starts_with("sae_pos_comp_subj"))

pos_subj_sae_AlgD_1 <- data %>%
  filter(disclosure == 1) %>%
  select(starts_with("sae_pos_comp_subj"))

anova2_plot <- make_anova2_plot(pos_subj_sae_AlgD_0, pos_subj_sae_AlgD_1)$plot

anova2_plot <- anova2_plot +
  # Cambiar nombres de las categorías en el eje X
  scale_x_discrete(labels = c("pos_subj_sae_AlgD_0" = "Sin revelación", 
                              "pos_subj_sae_AlgD_1" = "Con revelación")) +
  # Cambiar el título de la leyenda y los nombres de los grupos
  labs(
    title = "Comparación de comprensión subjetiva con manipulación disclosure de algoritmo",
    subtitle = "Análisis por condición de revelación",
    #x = "Condición de revelación",
    y = "Promedio"
  )+
  theme(plot.title = element_text(hjust = 0.1, face = "bold"))

anova2_plot
```

```{r disclosure_objective, echo=FALSE}
pos_obj_sae_AlgD_0 <- data %>%
  filter(disclosure == 0) %>%
  select(starts_with("sae_pos_comp_obj"))

pos_obj_sae_AlgD_1 <- data %>%
  filter(disclosure == 1) %>%
  select(starts_with("sae_pos_comp_obj"))

anova2_plot <- make_anova2_plot(pos_obj_sae_AlgD_0, pos_obj_sae_AlgD_1)$plot

anova2_plot <- anova2_plot +
  # Cambiar nombres de las categorías en el eje X
  scale_x_discrete(labels = c("pos_obj_sae_AlgD_0" = "Sin revelación", 
                              "pos_obj_sae_AlgD_1" = "Con revelación")) +
   # Cambiar el título de la leyenda y los nombres de los grupos
  labs(
    title = "Comparación de comprensión objetiva con manipulación disclosure de algoritmo",
    subtitle = "Análisis por condición de revelación",
    #x = "Condición de revelación",
    y = "Promedio"
  )+
  theme(plot.title = element_text(hjust = 0.1, face = "bold"))

anova2_plot
```

```{r disclosure_trust_func, echo=FALSE}
pos_trustFunc_sae_AlgD_0 <- data %>%
  filter(disclosure == 0) %>%
  select(starts_with(c("sae_pos_trust_belief_reliab", "sae_pos_trust_belief_func")))
pos_trustFunc_sae_AlgD_1 <- data %>%
  filter(disclosure == 1) %>%
  select(starts_with(c("sae_pos_trust_belief_reliab", "sae_pos_trust_belief_func")))

anova2_plot <- make_anova2_plot(pos_trustFunc_sae_AlgD_0, pos_trustFunc_sae_AlgD_1)$plot

anova2_plot <- anova2_plot +
  # Cambiar nombres de las categorías en el eje X
  scale_x_discrete(labels = c("pos_trustFunc_sae_AlgD_0" = "Sin revelación", 
                              "pos_trustFunc_sae_AlgD_1" = "Con revelación")) +
  # Cambiar el título de la leyenda y los nombres de los grupos
  labs(
    title = "Comparación de confianza funcional con manipulación disclosure de algoritmo",
    subtitle = "Análisis por condición de revelación",
    #x = "Condición de revelación",
    y = "Promedio"
  )+
  theme(plot.title = element_text(hjust = 0.1, face = "bold"))

anova2_plot
```

```{r disclosure_trust_moral, echo=FALSE}
pos_trustMoral_sae_AlgD_0 <- data %>%
  filter(disclosure == 0) %>%
  select(starts_with("sae_pos_trust_belief_help"))
pos_trustMoral_sae_AlgD_1 <- data %>%
  filter(disclosure == 1) %>%
  select(starts_with("sae_pos_trust_belief_help"))

anova2_plot <- make_anova2_plot(pos_trustMoral_sae_AlgD_0, pos_trustMoral_sae_AlgD_1)$plot

anova2_plot <- anova2_plot +
  # Cambiar nombres de las categorías en el eje X
  scale_x_discrete(labels = c("pos_trustMoral_sae_AlgD_0" = "Sin revelación", 
                              "pos_trustMoral_sae_AlgD_1" = "Con revelación")) +
  # Cambiar el título de la leyenda y los nombres de los grupos
  labs(
    title = "Comparación de confianza moral con manipulación disclosure de algoritmo",
    subtitle = "Análisis por condición de revelación",
    #x = "Condición de revelación",
    y = "Promedio"
  )+
  theme(plot.title = element_text(hjust = 0.1, face = "bold"))

anova2_plot
```

ANOVA H4: Explanations that include situational information associated with an automated system generate greater a) subjective and objective understanding as well as  b) functional and moral trust than an explanation that does not include this information.
```{r info sit_subjective, echo=FALSE}
pos_subj_sae_SI_0 <- data %>%
  filter(inf_situacional == 0) %>%
  select(starts_with("sae_pos_comp_subj"))

pos_subj_sae_SI_1 <- data %>%
  filter(inf_situacional == 1) %>%
  select(starts_with("sae_pos_comp_subj"))

anova2_plot <- make_anova2_plot(pos_subj_sae_SI_0, pos_subj_sae_SI_1)$plot

anova2_plot <- anova2_plot +
  # Cambiar nombres de las categorías en el eje X
  scale_x_discrete(labels = c("pos_subj_sae_SI_0" = "Sin revelación", 
                              "pos_subj_sae_SI_1" = "Con revelación")) +
   # Cambiar el título de la leyenda y los nombres de los grupos
  labs(
    title = "Comparación de comprensión subjetiva con manipulación info situacional",
    subtitle = "Análisis por condición de revelación",
    #x = "Condición de revelación",
    y = "Promedio"
  )+
  theme(plot.title = element_text(hjust = 0.1, face = "bold"))

anova2_plot
```

```{r info situc_objective, echo=FALSE}
pos_obj_sae_SI_0 <- data %>%
  filter(inf_situacional == 0) %>%
  select(starts_with("sae_pos_comp_obj"))
pos_obj_sae_SI_1 <- data %>%
  filter(inf_situacional == 1) %>%
  select(starts_with("sae_pos_comp_obj"))

anova2_plot <- make_anova2_plot(pos_obj_sae_SI_0, pos_obj_sae_SI_1)$plot

anova2_plot <- anova2_plot +
  # Cambiar nombres de las categorías en el eje X
  scale_x_discrete(labels = c("pos_obj_sae_SI_0" = "Sin revelación", 
                              "pos_obj_sae_SI_1" = "Con revelación")) +
   # Cambiar el título de la leyenda y los nombres de los grupos
  labs(
    title = "Comparación de comprensión objetiva con manipulación info situacional",
    subtitle = "Análisis por condición de revelación",
    #x = "Condición de revelación",
    y = "Promedio"
  )+
  theme(plot.title = element_text(hjust = 0.1, face = "bold"))

anova2_plot
```

```{r info situc_trust_func, echo=FALSE}
pos_trustFunc_sae_SI_0 <- data %>%
  filter(inf_situacional == 0) %>%
  select(starts_with(c("sae_pos_trust_belief_reliab", "sae_pos_trust_belief_func")))
pos_trustFunc_sae_SI_1 <- data %>%
  filter(inf_situacional == 1) %>%
  select(starts_with(c("sae_pos_trust_belief_reliab", "sae_pos_trust_belief_func")))

anova2_plot <- make_anova2_plot(pos_trustFunc_sae_SI_0, pos_trustFunc_sae_SI_1)$plot

anova2_plot <- anova2_plot +
  # Cambiar nombres de las categorías en el eje X
  scale_x_discrete(labels = c("pos_trustFunc_sae_SI_0" = "Sin revelación", 
                              "pos_trustFunc_sae_SI_1" = "Con revelación")) +
   # Cambiar el título de la leyenda y los nombres de los grupos
  labs(
    title = "Comparación de confianza funcional con manipulación info situacional",
    subtitle = "Análisis por condición de revelación",
    #x = "Condición de revelación",
    y = "Promedio"
  )+
  theme(plot.title = element_text(hjust = 0.1, face = "bold"))

anova2_plot
```

```{r info situac_trust_moral, echo=FALSE}
pos_trustMoral_sae_SI_0 <- data %>%
  filter(inf_situacional == 0) %>%
  select(starts_with("sae_pos_trust_belief_help"))

pos_trustMoral_sae_SI_1 <- data %>%
  filter(inf_situacional == 1) %>%
  select(starts_with("sae_pos_trust_belief_help"))

anova2_plot <- make_anova2_plot(pos_trustMoral_sae_SI_0, pos_trustMoral_sae_SI_1)$plot

anova2_plot <- anova2_plot +
  # Cambiar nombres de las categorías en el eje X
  scale_x_discrete(labels = c("pos_trustMoral_sae_SI_0" = "Sin revelación", 
                              "pos_trustMoral_sae_SI_1" = "Con revelación")) +
   # Cambiar el título de la leyenda y los nombres de los grupos
  labs(
    title = "Comparación de confianza moral con manipulación info situacional",
    subtitle = "Análisis por condición de revelación",
    #x = "Condición de revelación",
    y = "Promedio"
  )+
  theme(plot.title = element_text(hjust = 0.1, face = "bold"))

anova2_plot
```

ANOVA H5: Explanations that disclose human control information lead to greater a) subjective and objective understanding,  as well as b) functional and moral trust than an explanation that does not include this information.
```{r control humano_subjective, echo=FALSE}
pos_subj_sae_CH_0 <- data %>%
  filter(control_humano == 0) %>%
  select(starts_with("sae_pos_comp_subj"))

pos_subj_sae_CH_1 <- data %>%
  filter(control_humano == 1) %>%
  select(starts_with("sae_pos_comp_subj"))

anova2_plot <- make_anova2_plot(pos_subj_sae_CH_0, pos_subj_sae_CH_1)$plot

anova2_plot <- anova2_plot +
  # Cambiar nombres de las categorías en el eje X
  scale_x_discrete(labels = c("pos_subj_sae_CH_0" = "Sin revelación", 
                              "pos_subj_sae_CH_1" = "Con revelación")) +
   # Cambiar el título de la leyenda y los nombres de los grupos
  labs(
    title = "Comparación de comprensión subjetiva con manipulación control humano",
    subtitle = "Análisis por condición de revelación",
    #x = "Condición de revelación",
    y = "Promedio"
  )+
  theme(plot.title = element_text(hjust = 0.1, face = "bold"))

anova2_plot
```

```{r control humano_objective, echo=FALSE}
pos_obj_sae_CH_0 <- data %>%
  filter(control_humano == 0) %>%
  select(starts_with("sae_pos_comp_obj"))

pos_obj_sae_CH_1 <- data %>%
  filter(control_humano == 1) %>%
  select(starts_with("sae_pos_comp_obj"))

anova2_plot <- make_anova2_plot(pos_obj_sae_CH_0, pos_obj_sae_CH_1)$plot

anova2_plot <- anova2_plot +
  # Cambiar nombres de las categorías en el eje X
  scale_x_discrete(labels = c("pos_obj_sae_CH_0" = "Sin revelación", 
                              "pos_obj_sae_CH_1" = "Con revelación")) +
   # Cambiar el título de la leyenda y los nombres de los grupos
  labs(
    title = "Comparación de comprensión objetiva con manipulación control humano",
    subtitle = "Análisis por condición de revelación",
    #x = "Condición de revelación",
    y = "Promedio"
  )+
  theme(plot.title = element_text(hjust = 0.1, face = "bold"))

anova2_plot
```

```{r control humano_trust_func, echo=FALSE}
pos_trustFunc_sae_CH_0 <- data %>%
  filter(control_humano == 0) %>%
  select(starts_with(c("sae_pos_trust_belief_reliab", "sae_pos_trust_belief_func")))

pos_trustFunc_sae_CH_1 <- data %>%
  filter(control_humano == 1) %>%
  select(starts_with(c("sae_pos_trust_belief_reliab", "sae_pos_trust_belief_func")))

anova2_plot <- make_anova2_plot(pos_trustFunc_sae_CH_0, pos_trustFunc_sae_CH_1)$plot

anova2_plot <- anova2_plot +
  # Cambiar nombres de las categorías en el eje X
  scale_x_discrete(labels = c("pos_trustFunc_sae_CH_0" = "Sin revelación", 
                              "pos_trustFunc_sae_CH_1" = "Con revelación")) +
   # Cambiar el título de la leyenda y los nombres de los grupos
  labs(
    title = "Comparación de confianza funcional con manipulación control humano",
    subtitle = "Análisis por condición de revelación",
    #x = "Condición de revelación",
    y = "Promedio"
  )+
  theme(plot.title = element_text(hjust = 0.1, face = "bold"))

anova2_plot
```

```{r control humano_trust_moral, echo=FALSE}
pos_trustMoral_sae_CH_0 <- data %>%
  filter(control_humano == 0) %>%
  select(starts_with("sae_pos_trust_belief_help"))

pos_trustMoral_sae_CH_1 <- data %>%
  filter(control_humano == 1) %>%
  select(starts_with("sae_pos_trust_belief_help"))

anova2_plot <- make_anova2_plot(pos_trustMoral_sae_CH_0, pos_trustMoral_sae_CH_1)$plot

anova2_plot <- anova2_plot +
  # Cambiar nombres de las categorías en el eje X
  scale_x_discrete(labels = c("pos_trustMoral_sae_CH_0" = "Sin revelación", 
                              "pos_trustMoral_sae_CH_1" = "Con revelación")) +
   # Cambiar el título de la leyenda y los nombres de los grupos
  labs(
    title = "Comparación de confianza moral con manipulación control humano",
    subtitle = "Análisis por condición de revelación",
    #x = "Condición de revelación",
    y = "Promedio"
  )+
  theme(plot.title = element_text(hjust = 0.1, face = "bold"))

anova2_plot
```


#############################

```{r pressure, echo=FALSE}

```

```{r setup, include=FALSE}

```

