---
title: "Reporte de gráficos SAE"
format: html
editor: visual
---

```{r}
#| label: carga-y-filtro-datos
#| echo: true
#| message: false
#| warning: false

library(psych)
library(dplyr)
library(purrr)
library(ggplot2)
library(knitr)
library(kableExtra)
library(stats)

proc_env <- new.env(parent = globalenv())
source(here::here("script/proc_data.R"), local = proc_env)

if (exists("data", envir = proc_env)) {
  
  # Guardamos el total antes de filtrar
  total_inicial <- nrow(proc_env$data)
  
  # Filtramos: Nos quedamos con los que NO están marcados para eliminar (eliminado != 1)
  data <- proc_env$data %>% 
    dplyr::filter(eliminado != 1 | is.na(eliminado))
  
  # Calculamos finales
  final_analizar <- nrow(data)
  total_eliminados <- total_inicial - final_analizar
  
  # 4. Imprimir reporte de limpieza
  cat("\n--- REPORTE DE LIMPIEZA DE MUESTRA ---\n")
  cat("Total inicial de casos:       ", total_inicial, "\n")
  cat("Casos eliminados:             ", total_eliminados, "\n")
  cat("Total final para analizar:    ", final_analizar, "\n")
  cat("--------------------------------------\n")
  
} else {
  stop("Error: No se encontró el objeto 'data' dentro de proc_env. Revisa el script proc_data.R")
}
```

## Variables of interest

```{r}
#| label: variables-of-interest
#| echo: false
#| message: false
#| warning: false

sae_pre_comp_obj <- select(data, starts_with("sae_pre_comp_obj"))
sae_pos_comp_obj <- select(data, starts_with("sae_pos_comp_obj"))
sae_pre_comp_subj <- select(data, starts_with("sae_pre_comp_subj"))
sae_pos_comp_subj <- select(data, starts_with("sae_pos_comp_subj"))
sae_pre_trust_belief_reliab <- select(data, starts_with("sae_pre_trust_belief_reliab"))
sae_pos_trust_belief_reliab <- select(data, starts_with("sae_pos_trust_belief_reliab"))
sae_pre_trust_belief_func <- select(data, starts_with("sae_pre_trust_belief_func"))
sae_pos_trust_belief_func <- select(data, starts_with("sae_pos_trust_belief_func"))
sae_pre_trust_belief_help <- select(data, starts_with("sae_pre_trust_belief_help"))
sae_pos_trust_belief_help <- select(data, starts_with("sae_pos_trust_belief_help"))
sae_pre_trust_func_reliab <- select(data, starts_with("sae_pre_trust_func_reliab"))
sae_pos_trust_func_reliab <- select(data, starts_with("sae_pos_trust_func_reliab"))
sae_pre_trust_func_capab <- select(data, starts_with("sae_pre_trust_func_capab"))
sae_pos_trust_func_capab <- select(data, starts_with("sae_pos_trust_func_capab"))
sae_pre_trust_moral_ethi <- select(data, starts_with("sae_pre_trust_moral_ethi"))
sae_pos_trust_moral_ethi <- select(data, starts_with("sae_pos_trust_moral_ethi"))
sae_pre_trust_moral_sinc <- select(data, starts_with("sae_pre_trust_moral_sinc"))
sae_pos_trust_moral_sinc <- select(data, starts_with("sae_pos_trust_moral_sinc"))
```

## Descriptive statistics

```{r}
#| label: stats-table
#| echo: false
#| message: false
#| warning: false

# Function to calculate descriptive statistics - returns a tibble with the statistics
describe_stats <- function(data) {
  # Calculate the mean for each respondent (row-wise mean)
  row_means <- rowMeans(data, na.rm = TRUE)
  
  # Calculate overall statistics from these row means
  overall_mean <- mean(row_means, na.rm = TRUE)
  overall_median <- median(row_means, na.rm = TRUE)
  overall_sd <- sd(row_means, na.rm = TRUE)
  overall_min <- min(row_means, na.rm = TRUE)
  overall_max <- max(row_means, na.rm = TRUE)
  
  # Calculate Cronbach's alpha (psych::alpha) and extract only the raw_alpha
  alpha_val <- psych::alpha(data)$total$raw_alpha

  tibble(
    cronbach_alpha = alpha_val,
    mean = overall_mean,
    median = overall_median,
    std = overall_sd,
    min = overall_min,
    max = overall_max
  )
}

# For each of the variables, calculate cronbach's alpha, mean, median, std, min, max
pre_stats_obj_sae <- describe_stats(sae_pre_comp_obj)
pos_stats_obj_sae <- describe_stats(sae_pos_comp_obj)
pre_stats_subj_sae <- describe_stats(sae_pre_comp_subj)
pos_stats_subj_sae <- describe_stats(sae_pos_comp_subj)
pre_stats_trust_belief_reliab_sae <- describe_stats(sae_pre_trust_belief_reliab)
pos_stats_trust_belief_reliab_sae <- describe_stats(sae_pos_trust_belief_reliab)
pre_stats_trust_belief_func_sae <- describe_stats(sae_pre_trust_belief_func)
pos_stats_trust_belief_func_sae <- describe_stats(sae_pos_trust_belief_func)
pre_stats_trust_belief_help_sae <- describe_stats(sae_pre_trust_belief_help)
pos_stats_trust_belief_help_sae <- describe_stats(sae_pos_trust_belief_help)
pre_stats_trust_func_reliab_sae <- describe_stats(sae_pre_trust_func_reliab)
pos_stats_trust_func_reliab_sae <- describe_stats(sae_pos_trust_func_reliab)
pre_stats_trust_func_capab_sae <- describe_stats(sae_pre_trust_func_capab)
pos_stats_trust_func_capab_sae <- describe_stats(sae_pos_trust_func_capab)
pre_stats_trust_moral_ethi_sae <- describe_stats(sae_pre_trust_moral_ethi)
pos_stats_trust_moral_ethi_sae <- describe_stats(sae_pos_trust_moral_ethi)
pre_stats_trust_moral_sinc_sae <- describe_stats(sae_pre_trust_moral_sinc)
pos_stats_trust_moral_sinc_sae <- describe_stats(sae_pos_trust_moral_sinc)

# Create a table with the statistics for each variable
stats_table <- list(
  #sae_pre_comp_obj = pre_stats_obj_sae,
  #sae_pos_comp_obj = pos_stats_obj_sae,
  sae_pre_comp_subj = pre_stats_subj_sae,
  sae_pos_comp_subj = pos_stats_subj_sae,
  sae_pre_trust_belief_reliab = pre_stats_trust_belief_reliab_sae,
  sae_pos_trust_belief_reliab = pos_stats_trust_belief_reliab_sae,
  sae_pre_trust_belief_func = pre_stats_trust_belief_func_sae,
  sae_pos_trust_belief_func = pos_stats_trust_belief_func_sae,
  sae_pre_trust_belief_help = pre_stats_trust_belief_help_sae,
  sae_pos_trust_belief_help = pos_stats_trust_belief_help_sae,
  sae_pre_trust_func_reliab = pre_stats_trust_func_reliab_sae,
  sae_pos_trust_func_reliab = pos_stats_trust_func_reliab_sae,
  sae_pre_trust_func_capab = pre_stats_trust_func_capab_sae,
  sae_pos_trust_func_capab = pos_stats_trust_func_capab_sae,
  sae_pre_trust_moral_ethi = pre_stats_trust_moral_ethi_sae,
  sae_pos_trust_moral_ethi = pos_stats_trust_moral_ethi_sae,
  sae_pre_trust_moral_sinc = pre_stats_trust_moral_sinc_sae,
  sae_pos_trust_moral_sinc = pos_stats_trust_moral_sinc_sae
) |>
  imap_dfr(\(stats, var_name) dplyr::mutate(stats, Variable = var_name)) |>
  
  mutate(
    grupo = str_remove(Variable, "sae_pre_|sae_pos_"),
    momento = ifelse(str_detect(Variable, "pre"), 1, 2)
  ) |>
  # DEFINIMOS EL ORDEN DE LOS GRUPOS AQUÍ
  mutate(grupo = factor(grupo, levels = c(
    "comp_obj", "comp_subj", 
    "trust_belief_func", "trust_belief_reliab", # McKnight_Func
    "trust_belief_help",                        # McKnight_Moral
    "trust_func_capab", "trust_func_reliab",    # MDMT_Func
    "trust_moral_ethi", "trust_moral_sinc"      # MDMT_Moral
  ))) |>
  arrange(grupo, momento) |> 
  # ASIGNAMOS NOMBRES DESCRIPTIVOS AQUÍ
  mutate(Variable = case_when(
    #Variable == "sae_pre_comp_obj" ~ "Comprensión objetiva (pre)",
    #Variable == "sae_pos_comp_obj" ~ "Comprensión objetiva (post)",
    Variable == "sae_pre_comp_subj" ~ "Comprensión subjetiva (pre)",
    Variable == "sae_pos_comp_subj" ~ "Comprensión subjetiva (post)",
    Variable == "sae_pre_trust_belief_reliab" ~ "Trust McKnight_Func: Reliability (pre)",
    Variable == "sae_pos_trust_belief_reliab" ~ "Trust McKnight_Func: Reliability (post)",
    Variable == "sae_pre_trust_belief_func" ~ "Trust McKnight_Func: Functionality (pre)",
    Variable == "sae_pos_trust_belief_func" ~ "Trust McKnight_Func: Functionality (post)",
    Variable == "sae_pre_trust_belief_help" ~ "Trust McKnight_Moral: Helpfulness (pre)",
    Variable == "sae_pos_trust_belief_help" ~ "Trust McKnight_Moral: Helpfulness (post)",
    Variable == "sae_pre_trust_func_reliab" ~ "Trust MDMT_Func: Reliability (pre)",
    Variable == "sae_pos_trust_func_reliab" ~ "Trust MDMT_Func: Reliability (post)",
    Variable == "sae_pre_trust_func_capab" ~ "Trust MDMT_Func: Capacity (pre)",
    Variable == "sae_pos_trust_func_capab" ~ "Trust MDMT_Func: Capacity (post)",
    Variable == "sae_pre_trust_moral_ethi" ~ "Trust MDMT_Moral: Ethic (pre)",
    Variable == "sae_pos_trust_moral_ethi" ~ "Trust MDMT_Moral: Ethic (post)",
    Variable == "sae_pre_trust_moral_sinc" ~ "Trust MDMT_Moral: Sincerity (pre)",
    Variable == "sae_pos_trust_moral_sinc" ~ "Trust MDMT_Moral: Sincerity (post)",
    TRUE ~ Variable # Por si olvidas alguna, deja el nombre original
  )) |>
  select(Variable, everything(), -grupo, -momento) |>
  rename(
    "Cronbach alpha" = cronbach_alpha,
    "Mean" = mean,
    "Median" = median,
    "Std" = std,
    "Min" = min,
    "Max" = max
  )

stats_table %>%
  kbl(caption = "<b style='color:black; font-size:1.2em;'>Estadísticas descriptivas: dimensiones de comprensión y confianza</b>", 
      booktabs = TRUE, 
      centering = FALSE) %>%
  kable_styling(bootstrap_options = c("hover", "condensed"),
                full_width = F, 
                position = "left") %>%
  column_spec(1, width = "350px", bold = FALSE) %>%
  
  # Esto elimina esas líneas grises tenues que aún ves entre pre/post
  row_spec(0:nrow(stats_table), 
           extra_css = "border-top: none !important; border-bottom: none !important;padding-top: 2px !important; padding-bottom: 2px !important; line-height: 1 !important;") %>%
  
  # SEPARACIONES DE GRUPOS (Líneas gruesas)
  # Después de Comprensión (fila 2) y McKnight (fila 8)
  row_spec(c(2, 8), extra_css = "border-bottom: 2px solid black !important;") %>%
  
  # SALTOS DE LÍNEA (Separación funcional vs moral)
  # McKnight: Funcional termina en fila 6. MDMT: Funcional termina en fila 12.
  row_spec(c(6, 12), extra_css = "border-bottom: 1px solid #eee !important; padding-bottom: 10px !important;") %>%
  
  # ETIQUETAS DE GRUPO
  pack_rows("Dimensiones de comprensión", 1, 2) %>%
  pack_rows("Confianza (McKnight)", 3, 8) %>%
  pack_rows("Confianza (MDMT)", 9, 16)
```

## Hypothesis plots

```{r}
#| label: hypothesis-factors
#| echo: false
#| message: false
#| warning: false

data$disclosure <- as.factor(data$disclosure)
data$inf_situacional <- as.factor(data$inf_situacional)
data$control_humano <- as.factor(data$control_humano)
```

### H2 - algorithm disclosure (subjective understanding)

```{r}
#| label: h2-alg-disclosure-subjective
#| echo: false
#| message: false
#| warning: false

ttest_H2_AlgD_subj <- t.test(sae_comp_subjetiva_pos~disclosure, data = data)
plot(sae_comp_subjetiva_pos~disclosure, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H2_AlgD_subj$statistic)),
    sprintf("df = %.2f", unname(ttest_H2_AlgD_subj$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H2_AlgD_subj$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```

### H2 - algorithm disclosure (objective understanding)

```{r}
#| label: h2-alg-disclosure-objective
#| echo: false
#| message: false
#| warning: false

ttest_H2_AlgD_obj <- t.test(sae_comp_objetiva_pos~disclosure, data = data)
plot(sae_comp_objetiva_pos~disclosure, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H2_AlgD_obj$statistic)),
    sprintf("df = %.2f", unname(ttest_H2_AlgD_obj$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H2_AlgD_obj$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```

### H2 - algorithm disclosure (Functionality trust - McKnight)

```{r}
#| label: h2-disclosure-funct-trust-mcknight
#| echo: false
#| message: false
#| warning: false

ttest_H2_FE_trust_McKnight <- t.test(sae_conf_belief_funcional_pos~disclosure, data = data)
plot(sae_conf_belief_funcional_pos~disclosure, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H2_FE_trust_McKnight$statistic)),
    sprintf("df = %.2f", unname(ttest_H2_FE_trust_McKnight$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H2_FE_trust_McKnight$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```

### H2 - algorithm disclosure (Moral trust - McKnight)

```{r}
#| label: h2-disclosure-moral-trust-mcknight
#| echo: false
#| message: false
#| warning: false

ttest_H2_ME_trust_McKnight <- t.test(sae_conf_belief_moral_pos~disclosure, data = data)
plot(sae_conf_belief_moral_pos~disclosure, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H2_ME_trust_McKnight$statistic)),
    sprintf("df = %.2f", unname(ttest_H2_ME_trust_McKnight$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H2_ME_trust_McKnight$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```

### H2 - algorithm disclosure (Functionality trust - MDMT)

```{r}
#| label: h2-disclosure-funct-trust-MDMT
#| echo: false
#| message: false
#| warning: false

ttest_H2_FE_trust_MDMT <- t.test(sae_conf_word_funcional_pos~disclosure, data = data)
plot(sae_conf_word_funcional_pos~disclosure, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H2_FE_trust_MDMT$statistic)),
    sprintf("df = %.2f", unname(ttest_H2_FE_trust_MDMT$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H2_FE_trust_MDMT$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```

### H2 - algorithm disclosure (Moral trust - MDMT)

```{r}
#| label: h2-disclosure-moral-trust-MDMT
#| echo: false
#| message: false
#| warning: false

ttest_H2_ME_trust_MDMT <- t.test(sae_conf_word_funcional_pos~disclosure, data = data)
plot(sae_conf_word_funcional_pos~disclosure, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H2_ME_trust_MDMT$statistic)),
    sprintf("df = %.2f", unname(ttest_H2_ME_trust_MDMT$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H2_ME_trust_MDMT$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```

### H4 situational information (subjective understanding)

```{r}
#| label: H4-SI-subjective
#| echo: false
#| message: false
#| warning: false

ttest_H4_SI_subj <- t.test(sae_comp_subjetiva_pos~inf_situacional, data = data)
plot(sae_comp_subjetiva_pos~inf_situacional, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H4_SI_subj$statistic)),
    sprintf("df = %.2f", unname(ttest_H4_SI_subj$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H4_SI_subj$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```

### H4 situational information (objective understanding)

```{r}
#| label: H4-SI-objective
#| echo: false
#| message: false
#| warning: false

ttest_H4_SI_obj <- t.test(sae_comp_objetiva_pos~inf_situacional, data = data)
plot(sae_comp_objetiva_pos~inf_situacional, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H4_SI_obj$statistic)),
    sprintf("df = %.2f", unname(ttest_H4_SI_obj$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H4_SI_obj$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```

### H4 situational information (Functionality trust - McKnight)

```{r}
#| label: H4-SI-funct-trust-mcknight
#| echo: false
#| message: false
#| warning: false

ttest_H4_FE_trust_McKnight <- t.test(sae_conf_belief_funcional_pos~inf_situacional, data = data)
plot(sae_conf_belief_funcional_pos~inf_situacional, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H4_FE_trust_McKnight$statistic)),
    sprintf("df = %.2f", unname(ttest_H4_FE_trust_McKnight$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H4_FE_trust_McKnight$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```

### H4 situational information (Moral trust - McKnight)

```{r}
#| label: H4-SI-moral-trust-mcknight
#| echo: false
#| message: false
#| warning: false

ttest_H4_ME_trust_McKnight <- t.test(sae_conf_belief_moral_pos~inf_situacional, data = data)
plot(sae_conf_belief_moral_pos~inf_situacional, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H4_ME_trust_McKnight$statistic)),
    sprintf("df = %.2f", unname(ttest_H4_ME_trust_McKnight$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H4_ME_trust_McKnight$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```

### H4 situational information (Functionality trust - MDMT)

```{r}
#| label: h4-inf_situacional-funct-trust-MDMT
#| echo: false
#| message: false
#| warning: false

ttest_H4_FE_trust_MDMT <- t.test(sae_conf_word_funcional_pos~inf_situacional, data = data)
plot(sae_conf_word_funcional_pos~inf_situacional, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H4_FE_trust_MDMT$statistic)),
    sprintf("df = %.2f", unname(ttest_H4_FE_trust_MDMT$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H4_FE_trust_MDMT$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```

### H4 situational information (Moral trust - MDMT)

```{r}
#| label: h4-inf_situacional-moral-trust-MDMT
#| echo: false
#| message: false
#| warning: false

ttest_H4_ME_trust_MDMT <- t.test(sae_conf_word_funcional_pos~inf_situacional, data = data)
plot(sae_conf_word_funcional_pos~inf_situacional, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H4_ME_trust_MDMT$statistic)),
    sprintf("df = %.2f", unname(ttest_H4_ME_trust_MDMT$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H4_ME_trust_MDMT$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```

### H5 - control humano (subjective understanding)

```{r}
#| label: H5-CH-subjective
#| echo: false
#| message: false
#| warning: false

ttest_H5_CH_subj <- t.test(sae_comp_subjetiva_pos~control_humano, data = data)
plot(sae_comp_subjetiva_pos~control_humano, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H5_CH_subj$statistic)),
    sprintf("df = %.2f", unname(ttest_H5_CH_subj$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H5_CH_subj$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```

### H5 - control humano (objective understanding)

```{r}
#| label: H5-CH-objective
#| echo: false
#| message: false
#| warning: false

ttest_H5_CH_obj <- t.test(sae_comp_objetiva_pos~control_humano, data = data)
plot(sae_comp_objetiva_pos~control_humano, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H5_CH_obj$statistic)),
    sprintf("df = %.2f", unname(ttest_H5_CH_obj$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H5_CH_obj$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```

### H5 - control humano (Functionality trust - McKnight)

```{r}
#| label: H5-CH-funct-trust-mcknight
#| echo: false
#| message: false
#| warning: false

ttest_H5_FE_trust_McKnight <- t.test(sae_conf_belief_funcional_pos~control_humano, data = data)
plot(sae_conf_belief_funcional_pos~control_humano, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H5_FE_trust_McKnight$statistic)),
    sprintf("df = %.2f", unname(ttest_H5_FE_trust_McKnight$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H5_FE_trust_McKnight$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```

### H5 - control humano (Moral trust - McKnight)

```{r}
#| label: H5-CH-moral-trust-mcknight
#| echo: false
#| message: false
#| warning: false

ttest_H5_ME_trust_McKnight <- t.test(sae_conf_belief_moral_pos~control_humano, data = data)
plot(sae_conf_belief_moral_pos~control_humano, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H5_ME_trust_McKnight$statistic)),
    sprintf("df = %.2f", unname(ttest_H5_ME_trust_McKnight$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H5_ME_trust_McKnight$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```

### H5 - control humano (Functionality trust - MDMT)

```{r}
#| label: h5-control_humano-funct-trust-MDMT
#| echo: false
#| message: false
#| warning: false

ttest_H5_FE_trust_MDMT <- t.test(sae_conf_word_funcional_pos~control_humano, data = data)
plot(sae_conf_word_funcional_pos~control_humano, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H5_FE_trust_MDMT$statistic)),
    sprintf("df = %.2f", unname(ttest_H5_FE_trust_MDMT$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H5_FE_trust_MDMT$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```

### H5 - control humano (Moral trust - MDMT)

```{r}
#| label: h5-control_humano-moral-trust-MDMT
#| echo: false
#| message: false
#| warning: false

ttest_H5_ME_trust_MDMT <- t.test(sae_conf_word_funcional_pos~control_humano, data = data)
plot(sae_conf_word_funcional_pos~control_humano, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H5_ME_trust_MDMT$statistic)),
    sprintf("df = %.2f", unname(ttest_H5_ME_trust_MDMT$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H5_ME_trust_MDMT$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```
