---
title: "Presentacion-graphs-fonasa"
format: html
editor: visual
---

```{r}
#| label: setup
#| echo: false
#| message: false
#| warning: false

library(psych)
library(dplyr)
library(purrr)
library(ggplot2)

proc_env <- new.env(parent = globalenv())
source(here::here("script/proc_data.R"), local = proc_env)
data <- proc_env$data
stopifnot(exists("data", envir = proc_env), !is.null(data))
```

## Variables of interest

```{r}
#| label: variables-of-interest
#| echo: false
#| message: false
#| warning: false

pre_obj_fonasa <- select(data, starts_with("fonasa_pre_comp_obj"))
pos_obj_fonasa <- select(data, starts_with("fonasa_pos_comp_obj"))
pre_subj_fonasa <- select(data, starts_with("fonasa_pre_comp_subj"))
pos_subj_fonasa <- select(data, starts_with("fonasa_pos_comp_subj"))
pre_trust_belief_reliab_fonasa <- select(data, starts_with("fonasa_pre_trust_belief_reliab")) # Moral Ethic - McKnight
pos_trust_belief_reliab_fonasa <- select(data, starts_with("fonasa_pos_trust_belief_reliab")) # Moral Ethic - McKnight
pre_trust_belief_func_fonasa <- select(data, starts_with("fonasa_pre_trust_belief_func")) # Moral Ethic - McKnight
pos_trust_belief_func_fonasa <- select(data, starts_with("fonasa_pos_trust_belief_func")) # Moral Ethic - McKnight
pre_trust_func_reliab_fonasa <- select(data, starts_with("fonasa_pre_trust_func_reliab"))
pos_trust_func_reliab_fonasa <- select(data, starts_with("fonasa_pos_trust_func_reliab"))
pre_trust_func_capab_fonasa <- select(data, starts_with("fonasa_pre_trust_func_capab"))
pos_trust_func_capab_fonasa <- select(data, starts_with("fonasa_pos_trust_func_capab"))
pre_trust_moral_ethi_fonasa <- select(data, starts_with("fonasa_pre_trust_moral_ethi"))
pos_trust_moral_ethi_fonasa <- select(data, starts_with("fonasa_pos_trust_moral_ethi"))
pre_trust_moral_sinc_fonasa <- select(data, starts_with("fonasa_pre_trust_moral_sinc"))
pos_trust_moral_sinc_fonasa <- select(data, starts_with("fonasa_pos_trust_moral_sinc"))
pos_trust_belief_help_fonasa <- select(data, starts_with("fonasa_pos_trust_belief_help")) # Functional Ethic - McKnight
```

## Descriptive statistics

```{r}
#| label: stats-table
#| echo: false
#| message: false
#| warning: false

describe_stats <- function(data) {
  row_means <- rowMeans(data, na.rm = TRUE)

  overall_mean <- mean(row_means, na.rm = TRUE)
  overall_median <- median(row_means, na.rm = TRUE)
  overall_sd <- sd(row_means, na.rm = TRUE)
  overall_min <- min(row_means, na.rm = TRUE)
  overall_max <- max(row_means, na.rm = TRUE)

  alpha_val <- psych::alpha(data)$total$raw_alpha

  tibble(
    cronbach_alpha = alpha_val,
    mean = overall_mean,
    median = overall_median,
    std = overall_sd,
    min = overall_min,
    max = overall_max
  )
}

pre_stats_obj_fonasa <- describe_stats(pre_obj_fonasa)
pos_stats_obj_fonasa <- describe_stats(pos_obj_fonasa)
pre_stats_subj_fonasa <- describe_stats(pre_subj_fonasa)
pos_stats_subj_fonasa <- describe_stats(pos_subj_fonasa)
pre_stats_trust_belief_reliab_fonasa <- describe_stats(pre_trust_belief_reliab_fonasa)
pos_stats_trust_belief_reliab_fonasa <- describe_stats(pos_trust_belief_reliab_fonasa)
pre_stats_trust_belief_func_fonasa <- describe_stats(pre_trust_belief_func_fonasa)
pos_stats_trust_belief_func_fonasa <- describe_stats(pos_trust_belief_func_fonasa)
pre_stats_trust_func_reliab_fonasa <- describe_stats(pre_trust_func_reliab_fonasa)
pos_stats_trust_func_reliab_fonasa <- describe_stats(pos_trust_func_reliab_fonasa)
pre_stats_trust_func_capab_fonasa <- describe_stats(pre_trust_func_capab_fonasa)
pos_stats_trust_func_capab_fonasa <- describe_stats(pos_trust_func_capab_fonasa)
pre_stats_trust_moral_ethi_fonasa <- describe_stats(pre_trust_moral_ethi_fonasa)
pos_stats_trust_moral_ethi_fonasa <- describe_stats(pos_trust_moral_ethi_fonasa)
pre_stats_trust_moral_sinc_fonasa <- describe_stats(pre_trust_moral_sinc_fonasa)
pos_stats_trust_moral_sinc_fonasa <- describe_stats(pos_trust_moral_sinc_fonasa)
pos_stats_trust_belief_help_fonasa <- describe_stats(pos_trust_belief_help_fonasa)

stats_table <- list(
  pre_obj_fonasa = pre_stats_obj_fonasa,
  pos_obj_fonasa = pos_stats_obj_fonasa,
  pre_subj_fonasa = pre_stats_subj_fonasa,
  pos_subj_fonasa = pos_stats_subj_fonasa,
  pre_trust_belief_reliab_fonasa = pre_stats_trust_belief_reliab_fonasa,
  pos_trust_belief_reliab_fonasa = pos_stats_trust_belief_reliab_fonasa,
  pre_trust_belief_func_fonasa = pre_stats_trust_belief_func_fonasa,
  pos_trust_belief_func_fonasa = pos_stats_trust_belief_func_fonasa,
  pre_trust_func_reliab_fonasa = pre_stats_trust_func_reliab_fonasa,
  pos_trust_func_reliab_fonasa = pos_stats_trust_func_reliab_fonasa,
  pre_trust_func_capab_fonasa = pre_stats_trust_func_capab_fonasa,
  pos_trust_func_capab_fonasa = pos_stats_trust_func_capab_fonasa,
  pre_trust_moral_ethi_fonasa = pre_stats_trust_moral_ethi_fonasa,
  pos_trust_moral_ethi_fonasa = pos_stats_trust_moral_ethi_fonasa,
  pre_trust_moral_sinc_fonasa = pre_stats_trust_moral_sinc_fonasa,
  pos_trust_moral_sinc_fonasa = pos_stats_trust_moral_sinc_fonasa,
  pos_trust_belief_help_fonasa = pos_stats_trust_belief_help_fonasa
) |>
  imap_dfr(\(stats, var_name) dplyr::mutate(stats, Variable = var_name)) |>
  dplyr::select(Variable, dplyr::everything()) |>
  dplyr::arrange(Variable) |>
  dplyr::rename(
    "Mean" = mean,
    "Median" = median,
    "Std" = std,
    "Min" = min,
    "Max" = max,
    "Cronbach alpha" = cronbach_alpha,
  )

knitr::kable(stats_table, digits = 3)
```

## Hypothesis plots

```{r}
#| label: hypothesis-factors
#| echo: false
#| message: false
#| warning: false

data$ai_disclosure_fonasa <- as.factor(data$ai_disclosure_fonasa)
data$performance_fonasa <- as.factor(data$performance_fonasa)
data$control_humano_fonasa <- as.factor(data$control_humano_fonasa)
```

### H1 - AI Disclosure (Subjective competence)

```{r}
#| label: h1-ai-disclosure-subjective
#| echo: false
#| message: false
#| warning: false

ttest_H1_AID_subj <- t.test(fonasa_comp_subjetiva_pos ~ ai_disclosure_fonasa, data = data)
plot(fonasa_comp_subjetiva_pos ~ ai_disclosure_fonasa, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H1_AID_subj$statistic)),
    sprintf("df = %.2f", unname(ttest_H1_AID_subj$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H1_AID_subj$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```

### H1 - AI Disclosure (Objective competence)

```{r}
#| label: h1-ai-disclosure-objective
#| echo: false
#| message: false
#| warning: false

ttest_H1_AID_obj <- t.test(fonasa_comp_objetiva_pos ~ ai_disclosure_fonasa, data = data)
plot(fonasa_comp_objetiva_pos ~ ai_disclosure_fonasa, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H1_AID_obj$statistic)),
    sprintf("df = %.2f", unname(ttest_H1_AID_obj$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H1_AID_obj$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```

### H1 - AI Disclosure (Moral trust - McKnight)

```{r}
#| label: h1-ai-disclosure-moral-trust-mcknight
#| echo: false
#| message: false
#| warning: false

ttest_H1_ME_trust_McKnight <- t.test(fonasa_conf_belief_moral_pos ~ ai_disclosure_fonasa, data = data)
plot(fonasa_conf_belief_moral_pos ~ ai_disclosure_fonasa, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H1_ME_trust_McKnight$statistic)),
    sprintf("df = %.2f", unname(ttest_H1_ME_trust_McKnight$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H1_ME_trust_McKnight$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```

### H1 - AI Disclosure (Moral trust - MDMT)

```{r}
#| label: h1-ai-disclosure-moral-trust-mdmt
#| echo: false
#| message: false
#| warning: false

ttest_H1_ME_trust_MDMT <- t.test(fonasa_conf_word_moral_pos ~ ai_disclosure_fonasa, data = data)
plot(fonasa_conf_word_moral_pos ~ ai_disclosure_fonasa, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H1_ME_trust_MDMT$statistic)),
    sprintf("df = %.2f", unname(ttest_H1_ME_trust_MDMT$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H1_ME_trust_MDMT$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```

### H3 - Performance (Subjective competence)

```{r}
#| label: h3-performance-subjective
#| echo: false
#| message: false
#| warning: false

ttest_H3_P_subj <- t.test(fonasa_comp_subjetiva_pos ~ performance_fonasa, data = data)
plot(fonasa_comp_subjetiva_pos ~ performance_fonasa, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H3_P_subj$statistic)),
    sprintf("df = %.2f", unname(ttest_H3_P_subj$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H3_P_subj$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```

### H3 - Performance (Objective competence)

```{r}
#| label: h3-performance-objective
#| echo: false
#| message: false
#| warning: false

ttest_H3_P_obj <- t.test(fonasa_comp_objetiva_pos ~ performance_fonasa, data = data)
plot(fonasa_comp_objetiva_pos ~ performance_fonasa, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H3_P_obj$statistic)),
    sprintf("df = %.2f", unname(ttest_H3_P_obj$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H3_P_obj$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```

### H3 - Performance (Moral trust - McKnight)

```{r}
#| label: h3-performance-moral-trust-mcknight
#| echo: false
#| message: false
#| warning: false

ttest_H3_ME_trust_McKnight <- t.test(fonasa_conf_belief_moral_pos ~ performance_fonasa, data = data)
plot(fonasa_conf_belief_moral_pos ~ performance_fonasa, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H3_ME_trust_McKnight$statistic)),
    sprintf("df = %.2f", unname(ttest_H3_ME_trust_McKnight$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H3_ME_trust_McKnight$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```

### H3 - Performance (Moral trust - MDMT)

```{r}
#| label: h3-performance-moral-trust-mdmt
#| echo: false
#| message: false
#| warning: false

ttest_H3_ME_trust_MDMT <- t.test(fonasa_conf_word_moral_pos ~ performance_fonasa, data = data)
plot(fonasa_conf_word_moral_pos ~ performance_fonasa, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H3_ME_trust_MDMT$statistic)),
    sprintf("df = %.2f", unname(ttest_H3_ME_trust_MDMT$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H3_ME_trust_MDMT$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```

### H5 - Human control (Subjective competence)

```{r}
#| label: h5-human-control-subjective
#| echo: false
#| message: false
#| warning: false

ttest_H5_HC_subj <- t.test(fonasa_comp_subjetiva_pos ~ control_humano_fonasa, data = data)
plot(fonasa_comp_subjetiva_pos ~ control_humano_fonasa, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H5_HC_subj$statistic)),
    sprintf("df = %.2f", unname(ttest_H5_HC_subj$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H5_HC_subj$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```

### H5 - Human control (Objective competence)

```{r}
#| label: h5-human-control-objective
#| echo: false
#| message: false
#| warning: false

ttest_H5_HC_obj <- t.test(fonasa_comp_objetiva_pos ~ control_humano_fonasa, data = data)
plot(fonasa_comp_objetiva_pos ~ control_humano_fonasa, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H5_HC_obj$statistic)),
    sprintf("df = %.2f", unname(ttest_H5_HC_obj$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H5_HC_obj$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```

### H5 - Human control (Moral trust - McKnight)

```{r}
#| label: h5-human-control-moral-trust-mcknight
#| echo: false
#| message: false
#| warning: false

ttest_H5_HC_trust_McKnight <- t.test(fonasa_conf_belief_moral_pos ~ control_humano_fonasa, data = data)
plot(fonasa_conf_belief_moral_pos ~ control_humano_fonasa, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H5_HC_trust_McKnight$statistic)),
    sprintf("df = %.2f", unname(ttest_H5_HC_trust_McKnight$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H5_HC_trust_McKnight$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```

### H5 - Human control (Moral trust - MDMT)

```{r}
#| label: h5-human-control-moral-trust-mdmt
#| echo: false
#| message: false
#| warning: false

ttest_H5_HC_trust_MDMT <- t.test(fonasa_conf_word_moral_pos ~ control_humano_fonasa, data = data)
plot(fonasa_conf_word_moral_pos ~ control_humano_fonasa, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H5_HC_trust_MDMT$statistic)),
    sprintf("df = %.2f", unname(ttest_H5_HC_trust_MDMT$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H5_HC_trust_MDMT$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```

### H5 - Human control (Functional trust)

```{r}
#| label: h5-human-control-functional-trust
#| echo: false
#| message: false
#| warning: false

ttest_H5_HC_trust_func <- t.test(fonasa_conf_belief_funcional_pos ~ control_humano_fonasa, data = data)
plot(fonasa_conf_belief_funcional_pos ~ control_humano_fonasa, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H5_HC_trust_func$statistic)),
    sprintf("df = %.2f", unname(ttest_H5_HC_trust_func$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H5_HC_trust_func$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```

### H5 - Human control (Functional trust - MDMT)

```{r}
#| label: h5-human-control-functional-trust-mdmt
#| echo: false
#| message: false
#| warning: false

ttest_H5_HC_trust_func_MDMT <- t.test(fonasa_conf_word_funcional_pos ~ control_humano_fonasa, data = data)
plot(fonasa_conf_word_funcional_pos ~ control_humano_fonasa, data = data)
legend(
  "topright",
  legend = c(
    sprintf("t = %.3f", unname(ttest_H5_HC_trust_func_MDMT$statistic)),
    sprintf("df = %.2f", unname(ttest_H5_HC_trust_func_MDMT$parameter)),
    sprintf("p-value = %s", format.pval(ttest_H5_HC_trust_func_MDMT$p.value, digits = 3, eps = 0.001))
  ),
  bty = "n"
)
```
